{\sc underworlds}: Cascading Situation Assessment for Robots

### 2017-09-27 paper.tex
Anonymization

\uwds is a distributed and lightweight open-source
framework\footnote{\url{https://github.com/severin-lemaignan/underworlds}} that
enables robot programmers to build and refine spatial and temporal
models of the environment surrounding a robot in real-time. \uwds makes it possible to share
these world models amongst the software components running on the robot.
Additionally, \uwds enables users to represent and manipulate
\emph{multiple alternatives} to the current, perceived world model in a distributed manner. For
instance, the world with some objects filtered out; the world `viewed' from the
perspective of another agent; a hypothetical world resulting from the simulated
application of a plan, etc.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2}
    \caption{A user manipulating objects on top of an RFID mat (providing object
    localisation) with a NAO robot, while an operator monitors
    the interaction on a tablet that displays an {\tt uwds view} client.}

@@

\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor}
in order to conceptualise and visualise the spatial relations and visibility of
the physical objects that participants interact with. In one of the scenarios of this
project, participants are instructed by a NAO robot to manipulate a number of
Duplo-like animals on top of a printed background paper which serves as a
landscape (Figure~\ref{fig|l2torexample}). The robot instructions are based on
pedagogical strategies to promote spatial relation learning by object
manipulation. Such instructions include commands to place the elephant
\textit{on top} or \textit{next to} the cube, or put the giraffe \textit{inside}
the house.  To assess the performance, the robot and the operator need to
compute spatial relationships between objects from the visual perspective of the
participant.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{l2tor}
    \caption{Schema of the \uwds architecture used in the L2TOR project. }
    \label{fig|l2torarchitecture}
\end{figure}

@@

The L2TOR project features an additional scenario where the user performs the
manipulations on a tablet computer instead of using physical objects. To
accommodate this change, we replaced the object detection \uwds client with a 3D
virtual object detection while the rest of the system remains the same.

@@

This work has been supported by the EU H2020 Marie Sk\l odowska-Curie Actions
project DoRoThy (grant 657227) and the EU H2020 L2TOR project (grant 688014).

The authors also acknowledge the contribution of the HRI lab of LAAS-CNRS (where this
work debuted), and in particular, the influential ideas of Rachid Alami.

>>>>

\uwds is a distributed and lightweight open-source
%framework \footnote{\url{https://github.com/severin-lemaignan/underworlds}} that
framework \footnote{[GitHub URL hidden for blind review]} that
enables robot programmers to build and refine spatial and temporal
models of the environment surrounding a robot in real-time. \uwds makes it possible to share
these world models amongst the software components running on the robot.
Additionally, \uwds enables users to represent and manipulate
\emph{multiple alternatives} to the current, perceived world model in a distributed manner. For
instance, the world with some objects filtered out; the world `viewed' from the
perspective of another agent; a hypothetical world resulting from the simulated
application of a plan, etc.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2-blind}
    \caption{A user manipulating objects on top of an RFID mat (providing object
    localisation) with a NAO robot, while an operator monitors
    the interaction on a tablet that displays an {\tt uwds view} client [photo blurred for blind review].}

@@

%\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor}
\uwds has been used within the [hidden for blind review] project
in order to conceptualise and visualise the spatial relations and visibility of
the physical objects that participants interact with. In one of the scenarios of this
project, participants are instructed by a NAO robot to manipulate a number of
Duplo-like animals on top of a printed background paper which serves as a
landscape (Figure~\ref{fig|l2torexample}). The robot instructions are based on
pedagogical strategies to promote spatial relation learning by object
manipulation. Such instructions include commands to place the elephant
\textit{on top} or \textit{next to} the cube, or put the giraffe \textit{inside}
the house.  To assess the performance, the robot and the operator need to
compute spatial relationships between objects from the visual perspective of the
participant.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{l2tor}
    %\caption{Schema of the \uwds architecture used in the L2TOR project. }
    \caption{Schema of the \uwds architecture used in the [hidden for blind review] project. }
    \label{fig|l2torarchitecture}
\end{figure}

@@

%The L2TOR project features an additional scenario where the user performs the
The [hidden for blind review] project features an additional scenario where the user performs the
manipulations on a tablet computer instead of using physical objects. To
accommodate this change, we replaced the object detection \uwds client with a 3D
virtual object detection while the rest of the system remains the same.

@@

%This work has been supported by the EU H2020 Marie Sk\l odowska-Curie Actions
%project DoRoThy (grant 657227) and the EU H2020 L2TOR project (grant 688014).

%The authors also acknowledge the contribution of the HRI lab of LAAS-CNRS (where this
%work debuted), and in particular, the influential ideas of Rachid Alami.

[Hidden for blind review]
